\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-11 paper/main.tex
.

Finally, a potential source of differences in model performance is how
negatives are identified and treated during evaluation (and
training). There are few large sets of validated negative drug--target
interactions; consequently, many models (including \name{}) use all
unknown interactions as negatives. As there are many more negative
than positive interactions, negatives are then sub-sampled during
training resulting in a training set that is balanced between
positives and negatives (or a certain ratio is preserved). While this
is a reasonable strategy to deal with imbalanced data, it may be
problematic when the same sub-sampling is applied on the model's
evaluation set because it over-simplifies the evaluation process. The
performance differences is not usually visible when using ROC curves
but results in unrealistically high precision and therefore high area
under a precision-recall curve.

>>>>

Finally, a potential source of differences in model performance is how
negatives are identified and treated during evaluation (and
training). There are few large sets of validated negative drug--target
interactions; consequently, many models (including \name{}) use all
unknown interactions as negatives. As there are many more negative
than positive interactions, negatives are then sub-sampled during
training resulting in a training set that is balanced between
positives and negatives (or a certain ratio is preserved). While this
is a reasonable strategy to deal with imbalanced data, it may be
problematic when the same sub-sampling is applied on the model's
evaluation set because it over-simplifies the evaluation process. The
performance differences is not usually visible when using ROC curves
but results in unrealistically high precision and therefore high area
under a precision-recall curve\todo{I note that we do not report AUPR
  -- why not?}.
